A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-10 tex/codatadp.tex
More refactor.  Now somewhat clean.

We present the calculus in three parts.
In the first part we compute the bidirectional closure of $\Ec$,
in the second part we make inferences based on cyclicity and bisimilarity,
and in the third part we (when necessary) split on the constructor type for various terms in $\tEc$.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we will call an application of it to be \emph{non-terminal}),
or is $\bot$ (in which case we will call an application of it to be \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes a non-deterministic branching.
An application of a rule is \emph{redundant} if it is non-terminal and at least one branch in its conclusion does not add a new equality to $\Ec$.

@@

Recall that the $\mu$-notation can be used to represent (possibly cyclic) terms and values,
for instance, $\mu x. \const{C}( \const{0}, x )$ represents the cyclic value $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
Formally, we recursively define a $\mu$-term is either of the form
$\mu x. \const{C}( \vec t )$ for some constructor $\const{C} \in \Ctr$ and $\mu$-terms $\vec t$, 
or a variable $x$.
We assume all $\mu$-terms are \emph{well-typed}, which we defined recursively:
if the type of $\const{C}$ is $\vec \tau \rightarrow \upsilon$, 
then if $\vec v$ are well-type $\mu$-terms under the assumption that $x$ has type $\upsilon$,
then $\mu x. \const{C}( \vec v )$ is a well-typed term of type $\upsilon$.
We say a $\mu$-term is \emph{closed} if it contains no free variables.
We write $t \vsim s$ if $\mu$-terms $t$ and $s$ are syntactically equivalent modulo renaming of $\mu$-bound variables.
For convienience, we will use $\mu$-terms to refer to (classes of) values for both co-datatype and datatype terms,
where in the latter case, a $\mu$-term with a bound variable denotes an invalid term.
%where the latter case adds the restriction on $\mu$-terms $t$ that no subterms of $t$ contain are bound variables.

At the beginning of this step, 
we compute a mapping $\Val$ from equivalence classes to $\mu$-terms.
Informally, the terms mapped to by $\Val$ describe the (class of) values that terms in each equivalence class can take in the models of $\Ec$. 
For each equivalence class $\ec{x}$ of $\Ec$, we associate a fresh variable $v_{\ec{x}}$ of the same type as $x$ not occurring in $\tEc$,
and initially say that $\Val$ contains $\ec{x} \mapsto v_{\ec{x}}$ for each equivalence class $\ec{x}$ of $\Ec$ 
(in other words, there are initially no constraints on the values for terms).
Then, $\Val$ is updated by applying the following rule exhaustively:

@@

Here, we write $FV( \Val )$ to denote the free variables occurring in $\Val$, which
excludes variables that occur beneath $\mu$-binders.
It is straightforward to show that the height of terms produced as a result of this rule
is bounded by the number of equivalence classes of $\Ec$,
our construction of $\Val$ is terminating.

@@

Given $\Val$, the rules for cyclicity and bisimilar can be stated as follows, and are shown in Figure~\ref{fig:ab-rules}.
For cyclicity, if there is an equivalence class $\ec{t}$ of datatype type whose possible values $\mu x. t'$ are cyclic 
(as indicated by the assumption $x \in FV( t' )$),
then we can conclude that $\Ec$ is unsatisfiable.
For bisimilarity, if there are two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ 
of co-datatype type whose possible values $\Val \ec{t_1}$ and $\Val \ec{t_2}$ are equivalent modulo renaming of $\mu$-bound variables,
then we can conclude $t_1 \teq t_2$.
We demonstrate an application of this rule concretely with the following example.

\begin{example}
Let $\const{C}$ be a constructor of type $\tau_1 \times \tau_2 \rightarrow \tau_2$,
and let $\Ec$ be the set $\{ x \teq \const{C}(y,\const{C}(y,x)) \}$.
After applying the rules in Figure~\ref{fig:cc-rules} to completion, the equivalence classes of $\Ec$ are
$\{ x, \const{C}(y,\const{C}(y,x)) \}$, $\{ \const{C}(y,x) \}$, and $\{ y \}$.
Our construction of $\Val$ gives us:
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l}
\Val \ec{x} & = & 
\mu v_{\ec{x}}. \const{C}( v_{\ec{y}}, \mu v_{\ec{\const{C}(y,x)}}. \const{C}( v_{\ec{y}}, v_{\ec{x}} ) ) \\
\Val \ec{\const{C}(y,x)} & = & 
\mu v_{\ec{\const{C}(y,x)}}. \const{C}( v_{\ec{y}}, \mu v_{\ec{x}}. \const{C}( v_{\ec{y}}, v_{\ec{\const{C}(y,x)}} ) )
\end{array}\]
Notice that $\Val \ec{x}$ and $\Val \ec{\const{C}(y,x)}$ are syntactically equivalent for the renaming
$\{ v_{\ec{x}} \mapsto v_{\ec{\const{C}(y,x)}}, v_{\ec{\const{C}(y,x)}} \mapsto v_{\ec{x}} \}$,
and thus our calculus may infer the equality $x \teq \const{C}(y,x)$.
\qed
\end{example}

@@

%We first show that for any saturated node $\Fc$, 
%additional equalities $\Gc$ can be added to $\Fc$ such that each codatatype/datatype equivalence class of $\Fc \cup \Gc$ has a constructor term.
%For this purpose, we extend the calculus in this section.
%For a subset of equivalence classes $S$ of $\Ec$, write $\dpath{\Ec}{C,n}{S}$ to denote the set
%such that $e' \in \dpath{\Ec}{C,n}{S}$ if and only if there exists an $e \in S$ such that $e \rightarrow^{C}_n e'$ is induced by $\Ec$.

\begin{comment}
\begin{figure}[t]
\centering
\begin{tabular}{c}
\rn{O-Finish}
\(
\inferrule{
  \Ac := x
  \quad
  x : \tau
  \quad
  \tau \in \Nondata
  \quad
  c \not\in \tEc
}{
  \Ac := \emptyset \quad \Ec := \Ec \cup \{ x \teq c \}
}
\)
\\[3.7ex]
\rn{C-Finish}
\(
\inferrule{
  \Ac := x
  \quad
  x : \tau
  \quad
  \tau \in \Codata
  \quad
  C_i \in \Ctr^\tau
  \quad 
  C_i \not\in \{ C_j \mid d \in \Dc, C_j( \vec t ) \in d \}
}{
  \Ac := \emptyset \quad \Ec := \Ec \cup \{ x \teq C_i( \vec y ) \} \quad \Rc := \Rc \cup \vec y
}
\)
\\[3.7ex]
\rn{C-Rec}
\(
\inferrule{
  \Ac := x
  \quad
  x : \tau
  \quad
  \tau \in \Codata
  \quad
  C_i \in \Ctr^\tau
  \quad
  C_i \text{ infinite arg } j
}{
  \Ac := y_j \quad 
  \Ec := \Ec \cup \{ x \teq C_i( \vec y ) \} \quad 
  \Rc := \Rc \cup ( \vec y \setminus y_j ) \quad 
  \Dc := \dpath{\Ec}{C_i,j}{\Dc}
}
\)
\end{tabular}
\caption{Rules for completion.
}
\label{fig:completion-rules}
\end{figure}
\end{comment}

@@

\rem{Revise : now $\Val$ is constructed by calculus.}
Recall that the $\mu$-notation can be used to represent (possibly cyclic) values taken from an initial algebra, \rem{elaborate?} 
e.g. $\mu x. \const{C}( \const{0}, x )$ represents the infinite sequence $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
In this setting, a value can be viewed as a term-like structure where all subterms 
(which we will refer to as \emph{subvalues}) are either 
$\mu x. \const{C}( \vec v )$ for some constructor $\const{C}$ and subvalues $\vec v$
\footnote{We assume all values are well-typed. 
Here, the type of $\mu x. \const{C}( \vec v )$ and $x$ is the return type of $\const{C}$.}, or a variable $x$.
We will refer to values of this form as \emph{$\mu$-values}.
We say a $\mu$-value is \emph{closed} if it contains no free variables.
For convienience, we will represent the values of both datatypes and co-datatypes as closed $\mu$-values,
where the case of datatypes adds the restriction that none of its subvalues are variables.

We introduce the following notions concerning $\mu$-values.
First, we write $v \vsim u$ if $\mu$-values $v$ and $u$ are equivalent modulo renaming of $\mu$-bound variables.
The \emph{interpretation of subvalue $u$ in $v$} is the value $v\interp{u}^\emptyset$ returned by the following recursive procedure,
where $x \mapsto \mu x. C( \vec t ) \in v$ indicates that $\mu x. C( \vec t )$ is the subvalue of $v$ that binds this occurrence of variable $x$.
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l}
v\interp{x}^M & = & v\interp{\mu x. C( \vec t )}^M & x \not\in M, x \mapsto \mu x. C( \vec t ) \in v  \\
v\interp{x}^M & = & x & \text{otherwise} \\
v\interp{\mu x. C( \vec t )}^M & = & \mu x. C( v\interp{ \vec t }^{M \cup \{ x \}} ) & x \not\in M \\
v\interp{\mu x. C( \vec t )}^M & = & x & \text{otherwise}
\end{array}\]
Given a $\mu$-value $v$ of the form $\mu x. C( \vec w )$, 
a subvalue $u$ of $v$ is a \emph{bisimilar subvalue} if and only if $v\interp{u}^\emptyset \sim v$.
We say $v$ is \emph{normal} if and only if all of its bisimilar subvalues are $x$,
and all of its strict subvalues that do not contain $v$ are also normal.
For instance, the value $v$ of the form $\mu x. \const{S}( \mu y. \const{S}( x ) )$ is not normal, 
since 
$v\interp{\mu y. \const{S}( x )}^\emptyset =$ 
$\mu y. \const{S}( v\interp{x}^{\{y\}} ) =$ 
$\mu y. \const{S}( v\interp{\mu x. \const{S}( \mu y. \const{S}( x ) ) }^{\{y\}} ) =$ 
$\mu y. \const{S}( \mu x. \const{S}( v\interp{\mu y. \const{S}( x )}^{\{x,y\}} ) ) =$ 
$\mu y. \const{S}( \mu x. \const{S}( y ) )$,
which is equivalent to $v$ modulo the renaming $\{ x \mapsto y, y \mapsto x \}$.
For any $\mu$-value $v$ of the form $\mu x. C( \vec w )$, we may recursively construct a normal value $\nf{v}$
(which we will call the \emph{normal form for $v$})
that is observationally equivalent to $v$.
We construct $\nf{v}$ by replacing all of the bisimilar subvalues of $v$ with $x$,
and by replacing all of the non-normal closed subvalues of $v$ with their corresponding normal forms.
For instance, $\nf{(\mu x. \const{S}( \mu y. \const{S}( x ) ))} = \mu x. \const{S}( x )$.

@@

We construct a model $\M$ of $\thD$ that interprets constructors and correctly-applied selectors in the obvious way,
interprets wrongly-applied selectors based on equality information in $\Fc$,
interprets the variables and $x$ of $\Fc$ based on a mapping $\Val$ from the equivalence classes of $\Fc$ to values.
Initially, $\Val$ contains $\ec{x} \mapsto v_{\ec{x}}$ for each equivalence class $\ec{x}$ of $\Fc$,
where $v_{\ec{x}}$ is a fresh variable of the same type as $x$ not occurring in $\Fc$.
Then, $\Val$ is updated according to the following rules:

\rn{Ind}
\(
\inferrule{
  v_{\ec{x}} \in FV( \Val )
  \quad
  C( t_1, \ldots, t_n ) \in \ec{x}
  \quad
  C \in \Ctr
}{
  \Val := \Val \{ v_{\ec{x}} \mapsto \mu v_{\ec{x}}. C( v_{\ec{t_1}}, \ldots, v_{\ec{t_n}} ) \}
}
\)

\rn{Base}
\(
\inferrule{
  v_{\ec{x}} \in FV( \Val )
  \quad
  c \not\sim c' \text{ for all } c' \in \vrange(\Val)
}{
  \Val := \Val \{ v_{\ec{x}} \mapsto c \}
}
\)

\rem{define $\sim$}

In the rule \rn{Ind}, we write $FV( \Val )$ to denote the free variables occurring in $\Val$.
Notice that this excludes variables beneath $\mu$-binders.
As an example,
say that $\Fc$ contains equivalence classes $\ec{x}$ and $\ec{y}$ where $\const{C}(z,x) \in \ec{y}$ and $\const{C}(w,y) \in \ec{x}$, where $z$ and $w$ are variables of integer type.
A possible application of the above rules, showing the state of $\Val$ after each application, is as follows:
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l}
\hline
\text{Rule} & \multicolumn{4}{c}{\Val} \ 
\\
\hline
& \{ & \ec{x} \mapsto v_{\ec{x}}, & \ec{z} \mapsto v_{\ec{z}}, \\
&    & \ec{y} \mapsto v_{\ec{y}}, & \ec{w} \mapsto v_{\ec{w}} & \} \\
\rn{Ind} \ec{x}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, v_{\ec{y}} ), & \ec{z} \mapsto v_{\ec{z}}, \\
&    & \ec{y} \mapsto v_{\ec{y}}, & \ec{w} \mapsto v_{\ec{w}} & \} \\
\rn{Ind} \ec{y}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ) ), & \ec{z} \mapsto v_{\ec{z}}, \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ), & \ec{w} \mapsto v_{\ec{w}} & \} \\
\rn{Ind} \ec{x}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, v_{\ec{x}} ) ), & \ec{z} \mapsto v_{\ec{z}}, \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( v_{\ec{z}}, \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, v_{\ec{y}} ) ), & \ec{w} \mapsto v_{\ec{w}} & \} \\
\rn{Base} \ec{z}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, \mu v_{\ec{y}}. \const{C}( \const{0}, v_{\ec{x}} ) ), & \ec{z} \mapsto \const{0}, \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( \const{0}, \mu v_{\ec{x}}. \const{C}( v_{\ec{w}}, v_{\ec{y}} ) ), & \ec{w} \mapsto v_{\ec{w}} & \} \\
\rn{Base} \ec{w}
& \{ & \ec{x} \mapsto \mu v_{\ec{x}}. \const{C}( \const{1}, \mu v_{\ec{y}}. \const{C}( \const{0}, v_{\ec{x}} ) ), & \ec{z} \mapsto \const{0}, \\
&    & \ec{y} \mapsto \mu v_{\ec{y}}. \const{C}( \const{0}, \mu v_{\ec{x}}. \const{C}( \const{1}, v_{\ec{y}} ) ), & \ec{w} \mapsto \const{1} & \} \\
\end{array}\]

In our construction, the rule \rn{Ind} is first applied exhaustively.
Since the height of any value mapped to by $\Val$ is bounded by the number of equivalence classes of $\Fc$,
the rule \rn{Ind} can be applied only a finite number of times.
Second, \rn{Base} is applied exhaustively.
Since \rn{Base} removes one variable from the set $FV( \Val )$ and does not add any additional variables to $FV( \Val )$, 
the rule \rn{Base} can only be applied a finite number of times and does not trigger any new applications of \rn{Ind}.

We first argue that $\Val$ contains only ground values.
First, since \rn{Split} does not apply to $\Fc$,
all equivalence classes of finite type contain constructor terms.
Thus, after applying \rn{Ind} exhaustively, the free variables of $\Val$ all have infinite type.

>>>>

We present the calculus in three parts.
In the first part we compute the bidirectional closure of $\Ec$,
in the second part we make inferences based on cyclicity and bisimilarity,
and in the third part (when necessary) we branch on constructor types for various terms in $\tEc$.
Following the conventions from~\cite{}, 
the derivation rules of our calculus are given in \emph{guarded assignment form},
where a rule can be applied to $\Ec$ if it meets all of the specified preconditions for $\Ec$.
The conclusion of a rule either describes equalities to be added to $\Ec$ (in which case we will call an application of it to be \emph{non-terminal}),
or is $\bot$ (in which case we will call an application of it to be \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$, which denotes a non-deterministic branching.
An application of a rule is \emph{redundant} if it is non-terminal and at least one branch in its conclusion does not add a new equality to $\Ec$.

@@

Recall that the $\mu$-notation can be used to represent (possibly cyclic) terms and values,
for instance, $\mu x. \const{C}( \const{0}, x )$ represents the cyclic value $\const{C}( \const{0}, \const{C}( \const{0}, \ldots ))$.
Formally, we recursively define a $\mu$-term is either of the form
$\mu x. \const{C}( \vec t )$ for some constructor $\const{C} \in \Ctr$ and $\mu$-terms $\vec t$, 
or a variable $x$.
We consider only $\mu$-terms that are \emph{well-typed}, which we define recursively:
if the type of $\const{C}$ is $\vec \tau \rightarrow \upsilon$, 
then if $\vec v$ are well-type $\mu$-terms under the assumption that $x$ has type $\upsilon$,
then $\mu x. \const{C}( \vec v )$ is a well-typed term of type $\upsilon$.
We say a $\mu$-term is \emph{closed} if it contains no free variables.
We write $t \vsim s$ if $\mu$-terms $t$ and $s$ are syntactically equivalent modulo renaming of $\mu$-bound variables.
For convienience, we will use $\mu$-terms to refer to (classes of) values for both co-datatype and datatype terms,
where in the latter case, a $\mu$-term with a bound variable denotes an invalid term.
%where the latter case adds the restriction on $\mu$-terms $t$ that no subterms of $t$ contain are bound variables.

At the beginning of this step, 
we compute a mapping $\Val$ from equivalence classes to $\mu$-terms.
Informally, the terms mapped to by $\Val$ describe the (class of) values that terms in each equivalence class can take in the models of $\Ec$. 
For each equivalence class $\ec{x}$ of $\Ec$, we associate a fresh variable $v_{\ec{x}}$ of the same type as $x$ not occurring in $\tEc$,
and initially say that $\Val$ contains $\ec{x} \mapsto v_{\ec{x}}$ for each equivalence class $\ec{x}$ of $\Ec$ 
(in other words, there are initially no constraints on the values for any equivalence class).
Then, $\Val$ is updated by applying the following rule exhaustively:

@@

Here, we write $FV( \Val )$ to denote the free variables occurring in $\Val$, which
excludes variables that occur beneath $\mu$-binders.
It is straightforward to show that the height of terms produced as a result of this rule
is bounded by the number of equivalence classes of $\Ec$,
and thus our construction of $\Val$ is terminating.

@@

Given $\Val$, the rules for cyclicity and bisimilar (shown in Figure~\ref{fig:ab-rules}) can be stated as follows.
For cyclicity, if there is an equivalence class $\ec{t}$ of datatype type whose class of values $\Val \ec{t} = \mu x. t'$ are cyclic,
as indicated by the assumption $x \in FV( t' )$,
then we can conclude that $\Ec$ is unsatisfiable.
For bisimilarity, if there are two equivalence classes $\ec{t_1}$ and $\ec{t_2}$ 
of co-datatype type whose classes of values $\Val \ec{t_1}$ and $\Val \ec{t_2}$ are equivalent modulo renaming of $\mu$-bound variables,
then we can conclude $t_1 \teq t_2$.
We demonstrate an application of the rule for bisimilarity concretely with the following example.

\begin{example}
Let $\const{C}$ be a constructor of type $\tau_1 \times \tau_2 \rightarrow \tau_2$,
and let $\Ec$ be the set $\{ x \teq \const{C}(y,\const{C}(y,x)) \}$.
After applying the rules in Figure~\ref{fig:cc-rules} to completion, the equivalence classes of $\Ec$ are
$\{ x, \const{C}(y,\const{C}(y,x)) \}$, $\{ \const{C}(y,x) \}$, and $\{ y \}$.
We then construct $\Val$ using the aforementioned steps, after which we obtain:
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}r@{\hspace{.5em}}l@{\hspace{.5em}}r@{\hspace{.5em}}l}
\Val \ec{x} & = & 
\mu v_{\ec{x}}. & \const{C}( v_{\ec{y}}, & \mu v_{\ec{\const{C}(y,x)}}. & \const{C}( v_{\ec{y}}, v_{\ec{x}} ) ) \\
\Val \ec{\const{C}(y,x)} & = & 
\mu v_{\ec{\const{C}(y,x)}}. & \const{C}( v_{\ec{y}}, & \mu v_{\ec{x}}. & \const{C}( v_{\ec{y}}, v_{\ec{\const{C}(y,x)}} ) )
\end{array}\]
Notice that $\Val \ec{x}$ and $\Val \ec{\const{C}(y,x)}$ are syntactically equivalent for the renaming
$\{ v_{\ec{x}} \mapsto v_{\ec{\const{C}(y,x)}}, v_{\ec{\const{C}(y,x)}} \mapsto v_{\ec{x}} \}$,
and thus our calculus may infer $x \teq \const{C}(y,x)$.
Intuitively, this equality holds, since the values of $x$ and $\const{C}( y, x )$ are observationally equivalent for any value of $y$.
\qed
\end{example}

@@

@@

\rem{Revise : now $\Val$ is constructed by calculus.}

First, we require additional terminology concerning $\mu$-terms.
The \emph{interpretation of subvalue $u$ in $v$} is the value $v\interp{u}^\emptyset$ returned by the following recursive procedure,
where $x \mapsto \mu x. C( \vec t ) \in v$ indicates that $\mu x. C( \vec t )$ is the subvalue of $v$ that binds this occurrence of variable $x$.
\[\begin{array}{l@{\hspace{.5em}}l@{\hspace{.5em}}l@{\hspace{.5em}}l}
v\interp{x}^M & = & v\interp{\mu x. C( \vec t )}^M & x \not\in M, x \mapsto \mu x. C( \vec t ) \in v  \\
v\interp{x}^M & = & x & \text{otherwise} \\
v\interp{\mu x. C( \vec t )}^M & = & \mu x. C( v\interp{ \vec t }^{M \cup \{ x \}} ) & x \not\in M \\
v\interp{\mu x. C( \vec t )}^M & = & x & \text{otherwise}
\end{array}\]
Given a $\mu$-value $v$ of the form $\mu x. C( \vec w )$, 
a subvalue $u$ of $v$ is a \emph{bisimilar subvalue} if and only if $v\interp{u}^\emptyset \sim v$.
We say $v$ is \emph{normal} if and only if all of its bisimilar subvalues are $x$,
and all of its strict subvalues that do not contain $v$ are also normal.
For instance, the value $v$ of the form $\mu x. \const{S}( \mu y. \const{S}( x ) )$ is not normal, 
since 
$v\interp{\mu y. \const{S}( x )}^\emptyset =$ 
$\mu y. \const{S}( v\interp{x}^{\{y\}} ) =$ 
$\mu y. \const{S}( v\interp{\mu x. \const{S}( \mu y. \const{S}( x ) ) }^{\{y\}} ) =$ 
$\mu y. \const{S}( \mu x. \const{S}( v\interp{\mu y. \const{S}( x )}^{\{x,y\}} ) ) =$ 
$\mu y. \const{S}( \mu x. \const{S}( y ) )$,
which is equivalent to $v$ modulo the renaming $\{ x \mapsto y, y \mapsto x \}$.
For any $\mu$-value $v$ of the form $\mu x. C( \vec w )$, we may recursively construct a normal value $\nf{v}$
(which we will call the \emph{normal form for $v$})
that is observationally equivalent to $v$.
We construct $\nf{v}$ by replacing all of the bisimilar subvalues of $v$ with $x$,
and by replacing all of the non-normal closed subvalues of $v$ with their corresponding normal forms.
For instance, $\nf{(\mu x. \const{S}( \mu y. \const{S}( x ) ))} = \mu x. \const{S}( x )$.

@@

We construct a model $\M$ of $\thD$ that interprets constructors and correctly-applied selectors in the obvious way,
interprets wrongly-applied selectors based on equality information in $\Fc$,
interprets the variables and $x$ of $\Fc$ based on the valuation $\Val$ which we constructed in step two of our calculus.

Recall that $\Val$ was constructed as a mapping from the equivalence classes of $\Fc$ to $\mu$-terms.
We must first \emph{complete} $\Val$ so that it maps equivalence classes only to closed $\mu$-terms, that is, terms containing no free variables.
This is done by exhaustively applying of the following rule:

\(
\inferrule{
  v_{\ec{x}} \in FV( \Val )
  \quad
  c \not\sim c' \text{ for all } c' \in \vrange(\Val)
}{
  \Val := \Val \{ v_{\ec{x}} \mapsto c \}
}
\)
Since this rule removes one variable from the set $FV( \Val )$ and does not add any additional variables to $FV( \Val )$, 
it can only be applied a finite number of times.

We first argue that $\Val$ contains only to ground values (which include closed $\mu$-terms), in other words, $FV( \Val ) = \emptyset$.
First, since \rn{Split} does not apply to $\Fc$,
all equivalence classes of finite type contain constructor terms.
Thus, all variables in $FV( \Val )$ have infinite type.
